
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/riya-jaiswal-2060771b1/}{\Large Riya Jaiswal}} & {\textbf{Email :}}  \href{mailto:riyajaiswal2503@gmail.com}{riyajaiswal2503@gmail.com}\\
  \href{https://www.linkedin.com/in/riya-jaiswal-2060771b1/}{\color{blue}LinkedIn |} 
  \href{https://github.com/riyajaiswal25}{\color{blue}Github} & {\textbf{Location :}} Bangalore, India\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nitte Meenakshi Institute Of Technology}{Bangalore}
      {Bachelors of Engineering, Information Science and Engineering; \textbf{CGPA: 8.62/10}} {2020-2024}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
     \textbf{Languages}{: Java, Python, C, C++, R, SQL, MongoDB }
     }
 \resumeSubItem{}{
     \textbf{Technologies and Frameworks}{: Machine Learning, Deep Learning, EDA, NLP, Tensorflow, Keras }
    }
     \resumeSubItem{}{
     \textbf{Tools}{: Power BI, Eclipse, VS Code }
    }
    \resumeSubItem{}{
     \textbf{Other Skills}{: Data Analysis, Data Visualization, Problem Solving, Content Writing }
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {TechnoHacks}{Remote}
      {Data Analytics Intern}{2023/09 – 2023/10}
      \resumeItemListStart
        \resumeItem{}
          {Successfully performed \textbf{data cleaning}, removed missing values and outliers, enhancing data quality. }
        \resumeItem{}
        { Created clear and effective \textbf{visualizations using Matplotlib}, representing data distribution patterns.}
        \resumeItem{}
        { Developed an interactive \textbf{Power BI dashboard} for in-depth employee attrition analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {CodeClause}{Remote}
      { Data Science Intern}{2023/01 – 2023/02}
      \resumeItemListStart
      \resumeItem{}
          {Developed a deep learning model using \textbf{TensorFlow and Keras} for brain tumor detection during internship.}
        \resumeItem{}
          {Processed MRI images, created a dataset, and trained the model with \textbf{CNN architecture}.}
          \resumeItem{}
          {Achieved significant accuracy in tumor detection, contributing to healthcare technology advancement.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      { Potato Disease Classification}{\emph{\href{https://github.com/riyajaiswal25/potato-project-repo}{\color{blue}GitHub}}}      {\textbf{\underline{Tech Stack}} : \textit{Python}, \textit{Convolutional Neural Network (CNN)}, \textit{FastAPI}, \textit{Tensorflow}, \textit{Deep Learning}}

        \resumeItemListStart
        \resumeItem{}
          {Employed a CNN model to classify potato diseases with exceptional accuracy, resulting in \textbf{three distinct categories of diagnoses}, enabling early detection and targeted treatment strategies, revolutionizing crop health management practices. }
      \resumeItemListEnd
      \resumeSubheading
      { Car Price Prediction Model}{\emph{\href{https://github.com/riyajaiswal25/Car-Price-Predction-ML-Model}{\color{blue}GitHub}}}      {\textbf{\underline{Tech Stack}} : \textit{Python}, \textit{Machine Learning}, \textit{Linear Regression}, \textit{Flask}}

        \resumeItemListStart
        \resumeItem{}
          { This project aims to \textbf{predict the Price of an used Car} by taking it's Company name, it's Model name, Year of Purchase, and other parameters.}
      \resumeItemListEnd
      \resumeSubheading
      { Restaurant Review Sentiment Analysis}{\emph{\href{https://github.com/riyajaiswal25/Restaurant-Review-Sentiment-Analysis}{\color{blue}GitHub}}}      {\textbf{\underline{Tech Stack}} : \textit{Python}, \textit{Natural Language Processing (NLP)}, \textit{Transformers}, \textit{Flask}}

        \resumeItemListStart
        \resumeItem{}
          { Utilizing advanced NLP algorithms, categorized the reviews into \textbf{positive, negative, and neutral sentiments}, providing a nuanced understanding of the sentiments associated with different dining establishments.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%---------------------------------------
\section{Accomplishments}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
    \textbf{Won 2nd runner-up in Girls Geeks Hackathon 
}{organized at BMS College of Engineering. (Theme - \textbf{AI for Social Cause}), Built \textbf{Acne Grading Classifier}, an innovative initiative for the Dermatology Department. }
    }
    \resumeSubItem{}{
    \textbf{Microsoft Engage Mentee'22:}{ Demonstrated commitment to continuous learning and a proactive approach to career advancement.}
    }
    \resumeSubItem{}{
    \textbf{Amazon ML Summer School'23:}{ Participated in an intensive program on Machine Learning, gaining valuable insights into various subfields.}
    }
    
 \resumeSubHeadingListEnd
%-------------------------------------
%---------Certifications-------
\section{Certifications}
 \resumeSubHeadingListStart
  \resumeSubItem{}{\textbf{Machine Learning A-Z}}{\href{https://drive.google.com/file/d/1N-5QaSPBby3JTEe6bjQJGY1gutvxGpc2/view?usp=sharing}{\color{blue} Udemy}}
  \resumeSubItem{}{\textbf{ The Joy Of Computing Using Python}}{\href{https://drive.google.com/file/d/1sYRlMhdHhQCgebMU2hqGFiC2b32zrLKN/view}{\color{blue} NPTEL}}
  \resumeSubItem{}{\textbf{ Data Structures Using Java}}{\href{https://drive.google.com/file/d/1nYy_gFemO725agpw2RlTepC3caFDwPwW/view}{\color{blue} Coding Ninjas}}
  \resumeSubItem{}{\textbf{ Java Programming Fundamentals}}{\href{https://drive.google.com/file/d/1D53NM-mI55cAb-dIjFHgKQrs52YwwEtC/view?usp=sharing}{\color{blue} Infosys Springboard}}
 \resumeSubHeadingListEnd
\end{document}
